Tracking $p$-adic precision

### 2014-02-20 padicprec.tex
Update title and abstract

\title{$p$-adic precision}
%\author{Xavier Caruso, David Roe \& Tristan Vaccon}
\date\today

\maketitle
\begin{abstract}
We present a new method to handle $p$-adic precision (or more generally
precision over ultrametric fields) based on $p$-adic calculus.
We illustrate it by many examples and give a toy application to the
stable computation of the SOMOS 4 sequence.
\end{abstract}

>>>>

\title{Tracking $p$-adic precision}
%\author{Xavier Caruso, David Roe \& Tristan Vaccon}
\date\today

\maketitle
\begin{abstract}
We present a new method to propagate $p$-adic precision in computations, which also
applies to other ultrametric fields.
We illustrate it with many examples and give a toy application to the
stable computation of the SOMOS 4 sequence.
\end{abstract}
